Extracting all spectra for NEON mapped stems

### 2021-02-25 R/spectral-lib.Rmd
added package name
load sp library

```{r load-libraries, message=FALSE}
library(tidyverse)
library(neonUtilities)
#install.packages('remotes')
#remotes::install_github('NEONScience/NEON-geolocation/geoNEON', dependencies=TRUE)
library(geoNEON)
#install.packages('devtools')
#devtools::install_github('earthlab/neonhs')
library(neonhs)
library(dplyr)
library(here)
```

@@

```{r get-precise-locs, warning=FALSE}
vegmap <- getLocTOS(vegmap, "vst_mappingandtagging")

>>>>

```{r load-libraries, message=FALSE}
library(tidyverse)
library(neonUtilities)
#install.packages('remotes')
#remotes::install_github('NEONScience/NEON-geolocation/geoNEON', dependencies=TRUE)
library(geoNEON)
#install.packages('devtools')
#devtools::install_github('earthlab/neonhs')
library(neonhs)
library(dplyr)
library(here)
library(sp)
```

@@

```{r get-precise-locs, warning=FALSE}
vegmap <- geoNEON::getLocTOS(vegmap, "vst_mappingandtagging")
